PaperOutline_ACEsCog

### 2022-02-02 PaperOutline_ACEsCog.Rmd
add sensitivity, effect sizes, mediations, items
added sensitivity analyses, effect sizes, mediation analyses, item-level analyses

# Verify that correlation is low: it's 0.222
cor.test(all.data.complete$depriv,all.data.complete$emo_neglect)

# Test specificity
summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig 
summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # just depriv

p.adjust(c(0.005610,1.72e-09,0.0030,3.22e-08,0.0111,5.23e-09,0.323230,0.014438),method="bonferroni")

# try restricting age to ABCD range:
all.data.complete.ageres <- all.data.complete[all.data.complete$age<11.1,]
all.data.complete.ageres <- all.data.complete.ageres[all.data.complete.ageres$age>8.9,]
all.data.complete.ageres<-all.data.complete.ageres[all.data.complete.ageres$fat38a<50,]
all.data.complete.ageres$emo_neglect <- -rowMeans(data.frame(as.numeric(all.data.complete.ageres$fat38a)/3,as.numeric(all.data.complete.ageres$fat39a)/3),na.rm=TRUE) 
cor.test(all.data.complete.ageres$depriv,all.data.complete.ageres$emo_neglect)

# Test specificity
summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # both sig
summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # both sig
summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # both sig 
summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # just depriv

@@

@@

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_TP.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=TP)) +
  geom_point(colour=cols[2],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Temporal Processing") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_EF.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=EF)) +
  geom_point(colour=cols[4],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Exec. Fxn.") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_WM.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=WM)) +
  geom_point(colour=cols[8],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Working Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_IC.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=IC)) +
  geom_point(colour=cols[10],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Inhibitory Control") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()
```

@@

# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
# p.adjust(c(0.615, 2e-16,0.035,6.96e-11),method="bonferroni")
# # PC1 is related to physical neglect *** and trauma ***
# 
# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
# p.adjust(c(0.389, 7.47e-15,0.0096,4.39e-7),method="bonferroni")
# # PC1 is related to physical neglect ***, abuse *, and trauma ***
# 
# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
# p.adjust(c(0.034, 2e-16,0.014,6.18e-8),method="bonferroni")
# # PC3 is related to physical neglect *** and trauma ***
```

@@

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_PhysNeg_PC1.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC1)) +
  geom_point(colour=cols[2],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC1: General Cognition") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_PhysNeg_PC2.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC2)) +
  geom_point(colour=cols[4],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC2: Exec. Fxn.") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_PhysNeg_PC3.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC3)) +
  geom_point(colour=cols[8],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC3: Learning/Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_EmoNeg_PC1.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(abcd.data, aes(x=-acceptance,y=thompson_PC1)) +
  geom_point(colour=cols[2],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("PC1: General Cognition") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

>>>>

# # Test specificity
# summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
# summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
# summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig 
# summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # just depriv 
# 
# p.adjust(c(0.005610,1.72e-09,0.0030,3.22e-08,0.0111,5.23e-09,0.323230,0.014438),method="bonferroni")

# try restricting age to ABCD range:
all.data.complete.ageres <- all.data.complete[all.data.complete$age<11.1,]
all.data.complete.ageres <- all.data.complete.ageres[all.data.complete.ageres$age>8.9,]
all.data.complete.ageres<-all.data.complete.ageres[all.data.complete.ageres$fat38a<50,]
all.data.complete.ageres$emo_neglect <- -rowMeans(data.frame(as.numeric(all.data.complete.ageres$fat38a)/3,as.numeric(all.data.complete.ageres$fat39a)/3),na.rm=TRUE)

# Verify that correlation is low: it's 0.236
cor.test(all.data.complete.ageres$depriv,all.data.complete.ageres$emo_neglect)

# Test specificity
summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # just depriv
summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # just depriv
summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # just depriv
summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # neither

@@

# Get effect sizes
```{r}
library("effectsize")
model1<-anova(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres))
model2<-anova(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres))
model3<-anova(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres))
model4<-anova(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres))

eta2_emo_EF <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_phy_EF <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
eta2_emo_WM <- F_to_eta2(model2[3,]$`F value`,model2[3,]$NumDF,model2[3,]$DenDF)
eta2_phy_WM <- F_to_eta2(model2[4,]$`F value`,model2[4,]$NumDF,model2[4,]$DenDF)
eta2_emo_TP <- F_to_eta2(model3[3,]$`F value`,model3[3,]$NumDF,model3[3,]$DenDF)
eta2_phy_TP <- F_to_eta2(model3[4,]$`F value`,model3[4,]$NumDF,model3[4,]$DenDF)
eta2_emo_IC <- F_to_eta2(model4[3,]$`F value`,model4[3,]$NumDF,model4[3,]$DenDF)
eta2_phy_IC <- F_to_eta2(model4[4,]$`F value`,model4[4,]$NumDF,model4[4,]$DenDF)

eta2_emo_EF[1]
eta2_phy_EF[1]
eta2_emo_WM[1]
eta2_phy_WM[1]
eta2_emo_TP[1]
eta2_phy_TP[1]
eta2_emo_IC[1]
eta2_phy_IC[1]

@@

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_TP.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=TP)) +
  geom_point(position="jitter",colour=cols[2],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Temporal Processing") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_EF.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=EF)) +
  geom_point(position="jitter",colour=cols[4],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Exec. Fxn.") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_WM.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=WM)) +
  geom_point(position="jitter",colour=cols[8],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Working Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_IC.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=IC)) +
  geom_point(position="jitter",colour=cols[10],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Inhibitory Control") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()
```

# Demographics info
```{r}
# Gender (1, Male|2, Female)
sum(all.data.complete.ageres$gender==1,na.rm=TRUE)
round(sum(all.data.complete.ageres$gender==1,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
sum(all.data.complete.ageres$gender==2,na.rm=TRUE)
round(sum(all.data.complete.ageres$gender==2,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)

# Skin Color (1, White | 2, Black | 3, Between white and black (brown) | 4, Indigenous | 5, Asian | 99, Does not know)
sum(all.data.complete.ageres$skincolor==1,na.rm=TRUE)
round(sum(all.data.complete.ageres$skincolor==1,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
sum(all.data.complete.ageres$skincolor==2,na.rm=TRUE)
round(sum(all.data.complete.ageres$skincolor==2,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
sum(all.data.complete.ageres$skincolor==3,na.rm=TRUE)
round(sum(all.data.complete.ageres$skincolor==3,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
sum(all.data.complete.ageres$skincolor==4,na.rm=TRUE)
round(sum(all.data.complete.ageres$skincolor==4,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
sum(all.data.complete.ageres$skincolor==5,na.rm=TRUE)
round(sum(all.data.complete.ageres$skincolor==5,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)

# How far did the head of the family study?
# 99, Does not know|1, Without study (illiterate)|2, Elementary school incomplete (did not finish the former 8th grade)|3, Elementary school completed (finished the former 8th grade)|4, Incomplete high school (did not finish the former high school)|5, High school (finished the former high school)|6, Incomplete higher education (did not finish college)|7, Higher education (finished college)|8, Higher education with postgraduate studies (master's / doctorate / specialization)

# NOTE: get ab6 variable for this ^ from the scale dom_s06_treat_w0w2
```

@@

# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
# p.adjust(c(0.615, 2e-16,0.035,6.96e-11),method="bonferroni")
# # PC1 is related to physical neglect *** and trauma ***
# 
# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
# p.adjust(c(0.389, 7.47e-15,0.0096,4.39e-7),method="bonferroni")
# # PC1 is related to physical neglect ***, abuse *, and trauma ***
# 
# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
# p.adjust(c(0.034, 2e-16,0.014,6.18e-8),method="bonferroni")
# # PC3 is related to physical neglect *** and trauma ***

## Separate models for physical and emotional neglect:
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data)) # ***
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data)) # ***
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data)) # ***
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data)) # **
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data)) # .
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data)) # **
```

# Get effect sizes
```{r}
library("effectsize")
model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
model2<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
model3<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))

eta2_emo_PC1 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_phy_PC1 <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
eta2_emo_PC2 <- F_to_eta2(model2[3,]$`F value`,model2[3,]$NumDF,model2[3,]$DenDF)
eta2_phy_PC2 <- F_to_eta2(model2[4,]$`F value`,model2[4,]$NumDF,model2[4,]$DenDF)
eta2_emo_PC3 <- F_to_eta2(model3[3,]$`F value`,model3[3,]$NumDF,model3[3,]$DenDF)
eta2_phy_PC3 <- F_to_eta2(model3[4,]$`F value`,model3[4,]$NumDF,model3[4,]$DenDF)

eta2_emo_PC1[1]
eta2_phy_PC1[1]
eta2_emo_PC2[1]
eta2_phy_PC2[1]
eta2_emo_PC3[1]
eta2_phy_PC3[1]

# effect sizes for separate models of physical and emotional neglect:
model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
model2<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
model3<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
model4<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data))
model5<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data))
model6<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data))

eta2_emo_PC1 <- F_to_eta2(model4[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_phy_PC1 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_emo_PC2 <- F_to_eta2(model5[3,]$`F value`,model2[3,]$NumDF,model2[3,]$DenDF)
eta2_phy_PC2 <- F_to_eta2(model2[3,]$`F value`,model2[3,]$NumDF,model2[3,]$DenDF)
eta2_emo_PC3 <- F_to_eta2(model6[3,]$`F value`,model3[3,]$NumDF,model3[3,]$DenDF)
eta2_phy_PC3 <- F_to_eta2(model3[3,]$`F value`,model3[3,]$NumDF,model3[3,]$DenDF)

eta2_emo_PC1[1]
eta2_phy_PC1[1]
eta2_emo_PC2[1]
eta2_phy_PC2[1]
eta2_emo_PC3[1]
eta2_phy_PC3[1]

### Look at specific items within parental warmth and parental monitoring:
```{r}
abcd.data$crpbi_parent1_y<-as.numeric(abcd.data$crpbi_parent1_y)
abcd.data$crpbi_parent2_y<-as.numeric(abcd.data$crpbi_parent2_y)
abcd.data$crpbi_parent3_y<-as.numeric(abcd.data$crpbi_parent3_y)
abcd.data$crpbi_parent4_y<-as.numeric(abcd.data$crpbi_parent4_y)
abcd.data$crpbi_parent5_y<-as.numeric(abcd.data$crpbi_parent5_y)
abcd.data$parent_monitor_q1_y<-as.numeric(abcd.data$parent_monitor_q1_y)
abcd.data$parent_monitor_q2_y<-as.numeric(abcd.data$parent_monitor_q2_y)
abcd.data$parent_monitor_q3_y<-as.numeric(abcd.data$parent_monitor_q3_y)
abcd.data$parent_monitor_q4_y<-as.numeric(abcd.data$parent_monitor_q4_y)
abcd.data$parent_monitor_q5_y<-as.numeric(abcd.data$parent_monitor_q5_y)

important.variables3 <- abcd.data[,c("crpbi_parent1_y","crpbi_parent2_y","crpbi_parent3_y","crpbi_parent4_y","crpbi_parent5_y")]
colnames(important.variables3)<-c("Feel better talking worries","Smiles at me","Feel better when upset","Shows love","Easy to talk to")
corrplot(cor(important.variables3,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))

important.variables4 <- abcd.data[,c("parent_monitor_q1_y","parent_monitor_q2_y","parent_monitor_q3_y","parent_monitor_q4_y","parent_monitor_q5_y")]
colnames(important.variables4)<-c("Know where you are","Know who you're with","Know how to contact","Talk over plans","Dinner together")
corrplot(cor(important.variables4,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data)) # all significant *** (Q4 opp direction)
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data)) # all but Q3 sig (Q4 opp direction)
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data)) # all significant (Q4 opp direction)
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data)) # Q2, Q4, Q5 significant (Q5 opp direction)
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data)) # Q2, Q4, Q5 significant (Q5 opp direction)
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data)) # Q2, Q4, Q5 significant (Q5 opp direction)

# look for mediation: SES --> caregiving --> cognition
```{r}
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data))
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data))
# partial mediation!

summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data))
# partial mediation!

summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data))
# partial mediation!

# Simplify household income variable:
abcd.data$household.income.simple <- ifelse(abcd.data$household.income=="[>=100K]",1,0)

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data))
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data))
# partial mediation!

summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data))
# partial mediation!

summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data))
# partial mediation!

# Test for significance of mediation models with bootstrapping
bs_indir = c()
for (i in 1:10){
  thisSample <- sample(c(1:dim(abcd.data)[1]),dim(abcd.data)[1],replace=TRUE)
  pathc<-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data[thisSample,]))
  pathcp<-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data[thisSample,]))
  indir<-pathc$coefficients[4]-pathcp$coefficients[5]
  bs_indir <- c(bs_indir,indir)
}
t.test(bs_indir,conf.level=0.95)
## Significant partial mediation

bs_indir = c()
for (i in 1:10){
  thisSample <- sample(c(1:dim(abcd.data)[1]),dim(abcd.data)[1],replace=TRUE)
  pathc<-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data[thisSample,]))
  pathcp<-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data[thisSample,]))
  indir<-pathc$coefficients[4]-pathcp$coefficients[5]
  bs_indir <- c(bs_indir,indir)
}
t.test(bs_indir,conf.level=0.95)
## Significant partial mediation

bs_indir = c()
for (i in 1:10){
  thisSample <- sample(c(1:dim(abcd.data)[1]),dim(abcd.data)[1],replace=TRUE)
  pathc<-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data[thisSample,]))
  pathcp<-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data[thisSample,]))
  indir<-pathc$coefficients[4]-pathcp$coefficients[5]
  bs_indir <- c(bs_indir,indir)
}
t.test(bs_indir,conf.level=0.95)
## Significant partial mediation
```

@@

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_PhysNeg_PC1.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC1)) +
  geom_point(position="jitter",colour=cols[2],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC1: General Cognition") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_PhysNeg_PC2.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC2)) +
  geom_point(position="jitter",colour=cols[4],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC2: Exec. Fxn.") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_PhysNeg_PC3.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC3)) +
  geom_point(position="jitter",colour=cols[8],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC3: Learning/Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_EmoNeg_PC1.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(abcd.data, aes(x=-acceptance,y=thompson_PC1)) +
  geom_point(position="jitter",colour=cols[2],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("PC1: General Cognition") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

 png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_EmoNeg_PC2.png",
     width = 3000, 
     height = 3000,
     res = 850)
ggplot(abcd.data, aes(x=-acceptance,y=thompson_PC2)) +
  geom_point(position="jitter",colour=cols[4],size=1) +
  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("PC2: Exec. Fxn.") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
dev.off()
